Creating optimal conditions for reproducible data analysis in R with `fertile`

### 2020-02-27 fertile.Rmd
edits to methods section

As we have seen, many existing R packages focusing on reproducibility are designed in a way such that they can only be used prior to the start of a project, often for the purposes of creating an organized file structure or ordered file hierarchy. 
**fertile**, on the other hand, can be used at any stage in the data analysis workflow. It is designed to be used on data analyses organized as R Projects (i.e. folders containing a `.Rproj` file). Once an R Project is created, **fertile** can provide benefits at any time, both while coding as well as after the fact.
**fertile** operates in two modes: proactively (to prevent reproducibility mistakes from happening in the first place), and retroactively (analyzing code that has already been written for potential problems). 
**fertile** is available for download at [https://github.com/baumer-lab/fertile](https://github.com/baumer-lab/fertile)

@@

Proactively, the package identifies potential mistakes as they are made by the user and outputs an informative message as well as a recommended solution. For example, **fertile** catches when a user passes a potentially problematic file path---such as an absolute path, or a path that points to a location outside of the project directory---to a variety of common input/output functions.

@@

**fertile** is even more aggressive with functions (like `setwd()`) that are almost certain to break reproducibility---it causes them to throw errors.

@@

The proactive features are activated immediately after loading the **fertile** package and require no additional effort by the user.

In addition to the interactive warning system, **fertile** provides several useful utility functions. Among other things, these include functions to check the type of a file and a way to create a copy of a project in a temporary directory.

@@

>>>>

**fertile** looks to address these gaps, providing a simple, easy-to-learn reproducibility package that, rather than focusing intensely on a specific area, provides some information about a wide variety of aspects influencing reproducibility.

The package also provides flexibility--offering benefits to users at any stage in the data analysis workflow, unlike some other available packages which can only be used before the creation of a new project or after it is finished.

It is designed to be used on data analyses organized as R Projects (i.e. folders containing a `.Rproj` file). Once an R Project is created, **fertile** provides benefits throughout the data anlaysis process, both while coding as well as after the fact.

**fertile** achieves this by operating in two modes: proactively (to prevent reproducibility mistakes from happening in the first place), and retroactively (analyzing code that has already been written for potential problems).

@@

Proactively, the package identifies potential mistakes as they are made by the user and outputs an informative message as well as a recommended solution. For example, **fertile** catches when a user passes a potentially problematic file path---such as an absolute path, or a path that points to a location outside of the project directory---to a variety of common input/output functions operating on many different file types.

@@

**fertile** is even more aggressive with functions (like `setwd()`) that are almost certain to break reproducibility, causing them to throw errors that prevent their execution.

@@

The proactive features are activated immediately after loading the **fertile** package and require no additional effort by the user to access.

@@

\tiny
```{r, message = FALSE}
proj_analyze(".")
```
\normalsize

## Utility Functions

**fertile** also provides several useful utility functions. Among other things, these include functions to check the type of a file and a way to create a copy of a project in a temporary directory.
